\section{The SecureComputation module}\label{sec:computation}
The idea behind \texttt{SecureComputation} is exactly the same as \texttt{SecureFlow}. The difference relies on its aim. The former provides a way of working with pure data. \\
Taint analysis \cite{schwartz2010all}~\cite{newsome2005dynamic} is a well-known technique for dynamic detecting software vulnerabilities. However, this dynamic dimension is not fully sound when applied to modern software. It is so much complex that a full testing process is practically infeasible. Thus, we cannot just trust dynamic analysis. We need a statical check. \\
My version of this statical check is \texttt{SecureComputation} shown in a shortened form in Listing~\ref{lst:securecomp}.
\begin{lstlisting}[caption={SecureComputation module}, label={lst:securecomp}, breaklines=true]
data SC m a = SC a

type family MustBePure m :: Constraint
data P = P
data T = T
type instance (MustBePure P) = ()

open :: MustBePure m => SC m a -> a
open (SC a) = a

smap :: (MustBePure m, MustBePure m') => (a -> b) -> SC m a -> SC m' b
smap f (SC a) = SC $ f a

spure :: a -> SC m a
spure = SC

sapp :: (MustBePure m, MustBePure m') => SC m' (a -> b) -> SC m a -> SC m' b
sapp (SC f) sc = smap f sc

sreturn :: a -> SecureComputation m a
sreturn = spure

sbind :: (MustBePure m, MustBePure m') => SC m a -> (a -> SC m' b) -> SC m' b
sbind (SC a) f = f a
\end{lstlisting}
As one may notice, \texttt{SecureComputation} is based on the same type family method as \texttt{SecureFlow}. Basically, \texttt{P} and \texttt{T} are singleton types meaning \textit{Pure} and \textit{Tainted}. Naturally, only \texttt{P} is defined as an instance of the \texttt{MustBePure} constraint. \\
A \textit{SecureComputation} encapsulated value may be opened if and only if the \texttt{SecureComputation} holder is pure. Furthermore, computations on encapsulated values are allowed if and only if those values are pure (in the meaning that their containers are). \\
Again, \texttt{SecureComputation} is not a monad because of its type constraints. Making it a monad would be possible \cite{Sculthorpe:13:ConstrainedMonad}, as stated in Section~\ref{sec:unsecure}, but it is out of this paper scope. For the sake of simplicity I redefine functor, applicative and monad functions with another name (actually just adding \textit{s} as prefix) so that it might be used \textit{like} a monad. The meaning of those functions (\texttt{smap}, \texttt{spure}, \texttt{sapp} and \texttt{sbind}) is the usual one except for type constraints. Validity of a potential real instantiation would be also provable without considering type constraints. An example is given by the following proposition.
\input{sections/proofs/SCmonad}
\texttt{SecureComputation} is useful as a type for user-provided values. Listing~\ref{lst:unpureNat} shows how an input could be encapsulated and marked as tainted. Haskell, in fact, does not provide a function returning a \texttt{Num} (where \texttt{Num} is an abstract type class concretised by every type class representing a number, such as \texttt{Int} or \texttt{Float}). Thus one has to use \texttt{getLine}, which returns a \texttt{String}. In Section~\ref{sec:unsecure} I showed a way of validating this \texttt{String}. Here, contrariwise, no validation is performed on the user provided value; it is just marked as tainted (or not pure), so that it cannot be used as a parameter when a pure computation is required.
\begin{lstlisting}[caption={Tainted natural number},label={lst:unpureNat}, breaklines=true]
getUnpureNat :: IO (SecureComputation T String)
getUnpureNat = do n <- getLine
                  return $ spure n
\end{lstlisting}
Programmers can mark as tainted every value they want. They are also able to make differences among different input sources and values. That points \texttt{SecureComputation} flexibility out. For instance, recall the running example, and in particular the operations on stores. Every stored product has a price and a number representing its stocks. Increments or decrements on those numbers are allowed only with pure values. Otherwise a type error must be detected. A suitable general function should have the following type signature:\\
\texttt{SC P a -> String -> (a -> Store -> Store) -> SC P [Store] -> SC P [Store]}. \\
The parameters have meanings as follows:
\begin{enumerate}
	\item modification value (\textit{v});
	\item product name (\textit{p});
	\item the real modification function (\textit{f}) (for instance, \texttt{modifyPrice});
	\item a list of stores (\textit{s}).
\end{enumerate}
It returns a list of stores where \textit{p} has been modified according to \textit{f} based on \textit{v}. Note that \textit{v} and \textit{s} must be pure while it doesn't matter for \textit{p}. A type error is detected every time an unpure (or tainted) value is provided supposing it to be a pure one. If the code compiles and \texttt{SecureComputation} is cleverly used, there are not operations on pure data based on tainted one. 